Initial Analysis

### 2020-08-05 Scripts/Initial_Analysis.Rmd
FIxed images for publication

  # Total catch/Revenue shapefile
  World_sf_si_land <- World_land_sf %>%
    # st_transform(crs = 4326) %>% # 4326
    st_transform(crs = "+proj=eck4") %>%
    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
    left_join(Value_Trans_Country, by ="fishing_entity_id") %>% 
    filter(Variable %in% Variable_Selected)

  # Get the NA's to be grey
  Grey_land <- World_land_sf %>%  
    filter(!fishing_entity_id %in% World_sf_si_land$fishing_entity_id)

@@

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             y = -9050000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text",
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-8500000,-3200000,2000000,7000000,12500000)),
             y = -11000000,
             label = Labels,
             color="black",
             size=3,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-17000000,
             y = -9050000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-17000000,
             y = -11000000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      legend.box.margin = margin(t = -58, l = 120),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

    plot_all <- ggdraw() +
      # map
      draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
      # Revenue circular
      draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
      # Catch circular
      draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
      # Labeks
      draw_plot_label(label = c("A", "B"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(1, 0.45)
      ) +
      draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
                      size = 8,
                      x = c(0.330,0.485), 
                      y = c(0.31,0.29)
      )

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1000,5000,12000)

@@

  # Get legend for cowplot
legend_plot <- get_legend(Catch_Plot)
# Re-plot without legend
Catch_Plot <- Catch_Plot +
  theme(legend.position = "")
  p<- ggdraw() +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
  # Legend
  draw_plot(legend_plot, x = 0.2, y = 0.05, width = 0.59, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("A", "B"),
                  size = 15,
                  x = c(0.1, 0.55),
                  y = c(1, 1)
  ) +
  # draw_plot_label(
  #   label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
  #                 size = 6,
  #                 x = c(0.27,0.49),
  #                 y = c(0.66,0.63)
  # )
    draw_plot_label(
    label = c("Revenue     |     Catch",
              "(Thousand)  |     (Tons)",
              "(Per Km2)"),
                  size = 6,
                  x = c(0.41,
                        0.40,
                        0.48),
                  y = c(0.675,
                        0.65,
                        0.625)
  )

@@

# Just country names
country_names <- Clean_sau_eez_fes %>% 
  select(fishing_entity,fishing_entity_id) %>% 
  distinct()

@@

spp_plot <- ggdraw() +
  # Circular plot
  draw_plot(Spp_circular, x = 0, y = 0.305, width = 1, height = 0.60) +
  # Environmental maps
  draw_plot(Ecosystem_plots, x = 0.02, y = -0.029, width = 0.95, height = 0.26) +
  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 30,
                  x = c(0, 0), 
                  y = c(1, 0.27)
  )

@@

# Load Land shapefile
# World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>%
#   st_transform(crs = "+proj=eck4") %>%
#   # st_transform(crs = 4326) %>% # 4326
#   rename(fishing_entity = name_long) %>%
#   mutate(
#     fishing_entity = gsub(" and ", " & ",fishing_entity),
#     fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
#     fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
#     fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
#     fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
#     fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
#     fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
#     fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
#     fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
#     fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
#     fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
#     fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
#     fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
#     fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
#     fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
#     fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
#     fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
#     fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
#     fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
#     fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
#     fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
#     fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
#     fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
#     fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
#     fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
#     fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
#     fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
#     fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
#     fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
#     fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
#     fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
#     fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
#     fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
#     fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
#     fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
#     fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
#     fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
#     fishing_entity = gsub("United States", "USA",fishing_entity),
#     fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
#     fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
#     fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
#   )

>>>>

  # Total catch/Revenue shapefile
  World_sf_si_land <- World_land_sf %>%
    # st_transform(crs = 4326) %>% # 4326
    st_transform(crs = "+proj=eck4") %>%
    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
    filter(Variable %in% Variable_Selected)

  # Get the NA's to be grey
  Grey_land <- World_land_sf %>%  
    filter(!fishing_entity %in% World_sf_si_land$fishing_entity)

@@

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F,
    # labels = comma
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             y = -9050000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text",
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-8500000,-3200000,2000000,7000000,12500000)),
             y = -11000000,
             label = Labels,
             color="black",
             size=3,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-17000000,
             y = -9050000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-17000000,
             y = -11000000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      legend.box.margin = margin(t = -58, l = 120),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

    plot_all <- ggdraw() +
      # map
      draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
      # Revenue circular
      draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
      # Catch circular
      draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
      # Labeks
      draw_plot_label(label = c("a", "b"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(1, 0.45)
      ) +
      draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
                      size = 8,
                      x = c(0.330,0.485), 
                      y = c(0.31,0.29)
      )

@@

# Set manual breaks for bins
Map_Breaks <- c(-1,10,100,1,000,5000,12000)

@@

  # Get legend for cowplot
legend_plot <- get_legend(Catch_Plot)
# Re-plot without legend
Catch_Plot <- Catch_Plot +
  theme(legend.position = "")
  p<- ggdraw() +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
  # Legend
  draw_plot(legend_plot, x = 0.2, y = 0.05, width = 0.59, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("a", "b"),
                  size = 15,
                  x = c(0.1, 0.55),
                  y = c(1, 1)
  ) +
  # draw_plot_label(
  #   label = c("Revenue (Thousand USD) | Catch (Tons)","Per Km2"),
  #                 size = 6,
  #                 x = c(0.27,0.49),
  #                 y = c(0.66,0.63)
  # )
    draw_plot_label(
    label = c("Revenue     |     Catch",
              "(Thousand)  |     (Tons)",
              "(Per Km2)"),
                  size = 6,
                  x = c(0.41,
                        0.40,
                        0.48),
                  y = c(0.675,
                        0.65,
                        0.625)
  )

@@

# Just country names
country_names <- matching_names %>% 
  select(fishing_entity=sau_fishing_entity,fishing_entity_id) %>% 
  distinct()

@@

spp_plot <- ggdraw() +
  # Circular plot
  draw_plot(Spp_circular, x = 0, y = 0.305, width = 1, height = 0.60) +
  # Environmental maps
  draw_plot(Ecosystem_plots, x = 0.02, y = -0.029, width = 0.95, height = 0.26) +
  # Labeks
  draw_plot_label(label = c("a", "b"), 
                  size = 30,
                  x = c(0, 0), 
                  y = c(1, 0.27)
  )

@@

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>%
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  rename(fishing_entity = name_long) %>%
  mutate(
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
    fishing_entity = gsub("United States", "USA",fishing_entity),
    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
  )
